Investigating the Impact of Macroeconomic Indicators on the FTSE 250 Index and the Use of Machine Learning Methods to Forecast the Price of the FTSE 250 Index

### 2024-08-15 tex/paper.tex
title change

on the FTSE 250 Index Using Machine Learning Methods}
\author{Mateen Khan}
\date{\today}

@@

By introducing several modifications to the exact interpolation 
procedure, the radial basis function neural network
model is obtained, as presented in \figref{rbf_nn_architecture}. 
The network mapping takes the following form:

>>>>

on the FTSE 250 Index and the Use of Machine Learning Methods to Forecast the Price of the FTSE 250 Index}
\author{Mateen Khan}
\date{\today}

@@

By introducing several modifications to the exact interpolation 
procedure, the radial basis function neural network
model is obtained, as presented in Figure \ref{fig:rbf_nn_architecture}. 
The network mapping takes the following form:
